---
title: "Fanfic Scraper"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages
```{r message = FALSE, warning  = FALSE}
library(tidyverse)
library(rvest)
library(stringr)
library(xml2)
library(httr)
```

# String Splitting
```{r}
## Bespoke Stringsplitting function
strsplits <- function(x, splits, ...)
{
  for (split in splits)
  {
    x <- unlist(strsplit(x, split, ...))
  }
  return(x[!x == ""]) # Remove empty values
}
```

# Author Name
```{r}
## Extract Author Name
Author_Name <- function(input) {
  if (grepl("https://archiveofourown.org/users", input, fixed = FALSE)) {
    strsplit(gsub("https://archiveofourown.org/users/", "", input),
             "[/]")[[1]][1]
    
  } else {
    if (grepl("https://archiveofourown.org/", input, fixed = FALSE)) {
      print("Please enter a valid AO3 user profile link OR user name")
      
    } else{
      input
    }
  }
  
}
```


# Author Data

## Author Info

```{r}
GetAuthorInfo <- function(input) {
  ### Setup Author Info Table
  author_info <- data.frame(matrix(ncol = 2, nrow = 8)) %>%
    rename(Category = X1, Value = X2)
  
  author_info$Category <-
    c(
      "Name",
      "ID",
      "Join Date",
      "Profile URL",
      "Number of Works",
      "Works URL",
      "Number of Bookmarks",
      "Bookmarks URL"
    )
  
  ### Get Author Name from URL
  author_info[1, 2] <- Author_Name(input)
  
  ### Get Profile URL
  author_info[4, 2] <-
    paste0("https://archiveofourown.org/users/",
           author_info[1, 2],
           "/profile")
  
  ### Get Works URL
  author_info[6, 2] <-
    paste0("https://archiveofourown.org/users/",
           author_info[1, 2],
           "/works")
  
  ### Download Profile HTML Page
  author_profile <- GET(
    author_info[4, 2],
    user_agent(
      "Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/90.0.4430.93 Safari/537.36"
    )
  ) %>%
    read_html()
  
  profile <- author_profile %>%
    html_element(css = ".meta") %>%
    html_text2()
  
  ### Get Join Date
  author_info[3, 2] <-
    sub(".*I joined on *(.*?) *My user.*", "\\1", gsub("\n", " ",
                                                       gsub("[[:punct:]]", "", profile)))
  
  ### Get User ID
  author_info[2, 2] <- str_extract(gsub("\n", " ",
                                        gsub("[[:punct:]]", "", profile)), "My user ID is*.+") %>%
    str_replace("My user ID is ", "")
  
  
  
  ### Get Works Count
  author_info[5, 2] <- sub(".*Works *(.*?) *Series.*", "\\1",
                           gsub(
                             "\n",
                             " ",
                             gsub(
                               "[[:punct:]]",
                               "",
                               author_profile %>%
                                 html_element(css = "#dashboard") %>%
                                 html_text2()
                             )
                           ))
  
  ### Get Bookmark count
  author_info[7, 2] <- sub(".*Bookmarks *(.*?) *Collections.*",
                           "\\1",
                           gsub(
                             "\n",
                             " ",
                             gsub(
                               "[[:punct:]]",
                               "",
                               author_profile %>%
                                 html_element(css = "#dashboard") %>%
                                 html_text2()
                             )
                           ))
  
  ### Get Bookmarks URL
  author_info[8, 2] <-
    paste0("https://archiveofourown.org/users/",
           author_info[1, 2],
           "/bookmarks")
  
  author_info
}
```



## Works Info
```{r}
GetAuthorWorks <- function(input) {
  ### Download Works HTML Page
  author_works <- GET(
    paste0(
      "https://archiveofourown.org/users/",
      Author_Name(input),
      "/works"
    ),
    user_agent(
      "Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/90.0.4430.93 Safari/537.36"
    )
  ) %>%
    read_html()
  
  ### Setting up Works Table
  works_info <-
    sub(".*.Listing Works",
        "",
        gsub(
          "",
          "",
          author_works %>%
            html_element(css = "#main") %>%
            html_text2()
        )) %>%
    str_match_all("\\\n(.*?)by do not cache") %>%
    data.frame() %>%
    select(X2) %>%
    rowid_to_column() %>%
    rename(Titles = X2, Work = rowid)
  
  ### Works Page is a large string of text with all works data
  ### But Works are Preceded by the string "do not cache"
  ### Above function splits into DF by that string
  
  

  ### Big For-Loop for capturing all Works Summary Data
  
  
  if (0 == sub(".*Works *(.*?) *Series.*", "\\1",
               gsub(
                 "\n",
                 " ",
                 gsub(
                   "[[:punct:]]",
                   "",
                   author_works %>%
                   html_element(css = "#dashboard") %>%
                   html_text2()
                 )
               ))) {
    "N/A"
  } else{
    
    works_info$raw_text <- strsplits(author_works %>%
                                     html_element(css = "#main") %>%
                                     html_text2(),
                                   works_info$Titles)[-1]
  
  

### Get Works IDs and URLs
  works_ids <- author_works %>%
  html_elements(css = "h4 a") %>%
  html_attr("href") %>%
  data.frame() 

colnames(works_ids) <- "works_ids"

works_ids <- works_ids %>%
  filter(grepl("/works/", works_ids)) %>%
  mutate(works_ids = gsub("/works/", "", works_ids))

works_info$work_id <- works_ids$works_ids


### Get Works URLs

works_info$work_url <- paste0("https://archiveofourown.org/works/", works_info$work_id)


    for (i in 1:nrow(works_info)) {
      ### Word Count
      works_info$word_count[i] <-
        str_match(works_info$raw_text[i], "Words\\:\\n(.*?)\\\n")[1, 2]
      
      ### Language
      works_info$language[i] <-
        str_match(works_info$raw_text[i], "Language\\:\\n(.*?)\\\n")[1, 2]
      
      ### Chapter Count
      works_info$chapters[i] <-
        sub("/.*",
            "",
            str_match(works_info$raw_text[i], "Chapters\\:\\n(.*?)\\\n")[1, 2])
      
      ### Kudos Count
      works_info$kudos[i] <-
        str_match(works_info$raw_text[i], "Kudos\\:\\n(.*?)\\\n")[1, 2]
      
      ### Comments Count
      works_info$comments[i] <-
        str_match(works_info$raw_text[i], "Comments\\:\\n(.*?)\\\n")[1, 2]
      
      ### Hits Count
      works_info$hits[i] <-
        str_match(works_info$raw_text[i], "Hits\\:\\n(.*?)\\\n")[1, 2]
      
      ### Last Updated
      works_info$last_updated[i] <-
        str_match(works_info$raw_text[i], "\\n(.*?)\\\n\\nTags")[1, 2]
      
      ### (In)Complete Status
      works_info$status[i] <-
        str_match(works_info$raw_text[i],
                  paste0("\\n(.*?)\\\n\\n", works_info$last_updated[i]))[1, 2]
      
      ### Bookmarks Count
      works_info$bookmarks[i] <-
        str_match(works_info$raw_text[i], "Bookmarks\\:\\n(.*?)\\\n")[1, 2]
      
      ### Pairings (M/M, F/F, M/F, Multi, etc)
      works_info$pairings[i] <-
        str_match(works_info$raw_text[i],
                  paste0("\\n(.*?)\\\n", works_info$status[i]))[1, 2]
      
      ### Content Warnings
      works_info$warnings[i] <-
        str_match(works_info$raw_text[i],
                  paste0("\\n(.*?)\\\n", works_info$pairings[i]))[1, 2]
      
      ### Age Category (Mature, Teens, General)
      works_info$age_category[i] <-
        str_match(works_info$raw_text[i],
                  paste0("\\n(.*?)\\\n", works_info$warnings[i]))[1, 2]
      
      ### Fandoms
      works_info$fandoms[i] <-
        str_match(
          works_info$raw_text[i],
          paste0("\\nFandoms\\:(.*?)\\\n", works_info$age_category[i])
        )[1, 2]
    }
    works_info
  }
}
```

## Bookmarks
```{r}
GetAuthorBookmarks <- function(input) {
  ### Get bookmarks HTML Page
  bookmarks_html <- GET(
    paste0(
      "https://archiveofourown.org/users/",
      Author_Name(input),
      "/bookmarks"
    ),
    user_agent(
      "Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/90.0.4430.93 Safari/537.36"
    )
  ) %>%
    read_html()
  
  bookmarks <- bookmarks_html %>%
    html_element(css = "#main") %>%
    html_text2()
  
  ### Setting up Works Table
  bookmarks_info <-
    sub(".*.Listing Works",
        "",
        gsub("",
             "",
             bookmarks)) %>%
    str_match_all("\\\n(.*?)by do not cache") %>%
    data.frame() %>%
    select(X2) %>%
    rowid_to_column() %>%
    rename(Titles = X2, Work = rowid)
  
  ### Works Page is a large string of text with all works data
  ### But Works are Preceded by the string "do not cache"
  ### Above function splits into DF by that string
  
  




## Check for bookmarks if they even exist
  
  if (0 == sub(".*Bookmarks *(.*?) *Collections.*",
               "\\1",
               gsub(
                 "\n",
                 " ",
                 gsub(
                   "[[:punct:]]",
                   "",
                   bookmarks_html %>%
                   html_element(css = "#dashboard") %>%
                   html_text2()
                 )
               ))) {
    "N/A"
  } else {
    
    
      
  bookmarks_info$raw_text <- strsplits(bookmarks,
                                       "by do not cache")[-1]
  
### Get Works IDs
works_ids <- bookmarks_html %>%
  html_elements(css = "h4 a") %>%
  html_attr("href") %>%
  data.frame() 

colnames(works_ids) <- "works_ids"

works_ids <- works_ids %>%
  filter(grepl("/works/", works_ids)) %>%
  mutate(works_ids = gsub("/works/", "", works_ids))

bookmarks_info$work_id <- works_ids$works_ids

### Get Works URLs

bookmarks_info$work_url <- paste0("https://archiveofourown.org/works/", bookmarks_info$work_id)



    ### Big For-Loop for capturing all Bookmarks Summary Data
    for (i in 1:nrow(bookmarks_info)) {
      ### Word Count
      bookmarks_info$word_count[i] <-
        str_match(bookmarks_info$raw_text[i], "Words\\:\\n(.*?)\\\n")[1, 2]
      
      ### Language
      bookmarks_info$language[i] <-
        str_match(bookmarks_info$raw_text[i], "Language\\:\\n(.*?)\\\n")[1, 2]
      
      ### Chapter Count
      bookmarks_info$chapters[i] <-
        sub("/.*",
            "",
            str_match(bookmarks_info$raw_text[i], "Chapters\\:\\n(.*?)\\\n")[1, 2])
      
      ### Kudos Count
      bookmarks_info$kudos[i] <-
        str_match(bookmarks_info$raw_text[i], "Kudos\\:\\n(.*?)\\\n")[1, 2]
      
      ### Comments Count
      bookmarks_info$comments[i] <-
        str_match(bookmarks_info$raw_text[i], "Comments\\:\\n(.*?)\\\n")[1, 2]
      
      ### Hits Count
      bookmarks_info$hits[i] <-
        str_match(bookmarks_info$raw_text[i], "Hits\\:\\n(.*?)\\\n")[1, 2]
      
      ### Last Updated
      bookmarks_info$last_updated[i] <-
        str_match(bookmarks_info$raw_text[i], "\\n(.*?)\\\n\\nTags")[1, 2]
      
      ### (In)Complete Status
      bookmarks_info$status[i] <-
        str_match(
          bookmarks_info$raw_text[i],
          paste0("\\n(.*?)\\\n\\n", bookmarks_info$last_updated[i])
        )[1, 2]
      
      ### Bookmarks Count
      bookmarks_info$bookmarks[i] <-
        str_match(bookmarks_info$raw_text[i], "Bookmarks\\:\\n(.*?)\\\n")[1, 2]
      
      ### Pairings (M/M, F/F, M/F, Multi, etc)
      bookmarks_info$pairings[i] <-
        str_match(bookmarks_info$raw_text[i],
                  paste0("\\n(.*?)\\\n", bookmarks_info$status[i]))[1, 2]
      
      ### Content Warnings
      bookmarks_info$warnings[i] <-
        str_match(bookmarks_info$raw_text[i],
                  paste0("\\n(.*?)\\\n", bookmarks_info$pairings[i]))[1, 2]
      
      ### Age Category (Mature, Teens, General)
      bookmarks_info$age_category[i] <-
        str_match(bookmarks_info$raw_text[i],
                  paste0("\\n(.*?)\\\n", bookmarks_info$warnings[i]))[1, 2]
      
      ### Fandoms
      bookmarks_info$fandoms[i] <-
        str_match(
          bookmarks_info$raw_text[i],
          paste0(
            "\\nFandoms\\:(.*?)\\\n",
            bookmarks_info$age_category[i]
          )
        )[1, 2]
    }
    
    bookmarks_info
    
  }
}
```



## All
```{r}
GetAuthorAll <- function(input){
  list(GetAuthorInfo(input), 
       GetAuthorWorks(input), 
       GetAuthorBookmarks(input))
}
```


```{r}
author_works <- GET(
    paste0(
      "https://archiveofourown.org/users/",
      Author_Name("SometimeLonely"),
      "/works"
    ),
    user_agent(
      "Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36 (KHTML, like Gecko) Chrome/90.0.4430.93 Safari/537.36"
    )
  ) %>%
    read_html()
```



# TESTING AREA

## GetAuthorInfo

Results for both should be: an 8x2 table with all results filled in

### With Name
```{r}
GetAuthorInfo("AmandaWilkie")
```

### With URL
```{r}
GetAuthorInfo("https://archiveofourown.org/users/AmandaWilkie/pseuds/AmandaWilkie/bookmarks")
```


## GetAuthorBookmarks

### Author With Bookmarks

Result for both should be: A 14x18 table with all details filled in

#### Using Name
```{r}
GetAuthorBookmarks("yohjikammy")
```


#### Using URL
```{r}
GetAuthorBookmarks("https://archiveofourown.org/users/yohjikammy/pseuds/yohjikammy")
```


### Author Without Bookmarks

Result for both should be: "N/A"

#### Using Name
```{r}
GetAuthorBookmarks("AmandaWilkie")
```

#### Using URL
```{r}
GetAuthorBookmarks("https://archiveofourown.org/users/AmandaWilkie/pseuds/AmandaWilkie/bookmarks")
```



## GetAuthorWorks

### Authors with Works

Results for both should be: a 6x18 table with all details filled in

#### Using Name
```{r}
GetAuthorWorks("Sataroni")
```


#### Using URL
```{r}
GetAuthorWorks("https://archiveofourown.org/users/Sataroni/pseuds/Sataroni")
```


